### 2020-02-09 analysis/paper.Rmd
Renames debugging file as temp and adds placeholder paper markdown file

---
title: "Replication Project"
author: "Lauren Heintz, Ben Brodeur Mathieu, Will Wright and Tara Wilson"
date: "February 9, 2020"
output: bookdown::word_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2020-02-10 analysis/paper.Rmd
adding the RMD file with bibliography

@@
 ---
-title: "Replication Project"
-author: "Lauren Heintz, Ben Brodeur Mathieu, Will Wright and Tara Wilson"
-date: "February 9, 2020"
+title: "[Re] Marriage and happiness: Oishi, Kesebir, and Diener (2011)"
+author: "Lauren Heintz, Tara Wilson, Ben Mathieu, Will Wright"
+date: "`r format(Sys.time(), '%d %B, %Y')`"
 output: bookdown::word_document2
+bibliography: bibliography.bibtex
+link-citations: yes
+
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+``` {r setup, echo = FALSE}
+knitr::opts_chunk$set(
+  collapse = TRUE,
+  warning = FALSE,
+  message = FALSE,
+  echo = FALSE,
+  comment = "#>",
+  fig.path = "../figures")
+#knitr::read_chunk("src/my-external-code.R")
 ```
 
-## R Markdown
+# Introduction
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+# Methods
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+# Results
 
-```{r cars}
-summary(cars)
-```
+# Conclusion
 
-## Including Plots
+# References
 
-You can also embed plots, for example:
+Reference 1: @marriagehappiness  
+Reference 2: @data
 
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+---

### 2020-02-16 analysis/paper.Rmd
updates to RMD to add a function and added metadaata.yaml

@@
 ---
-title: "[Re] Marriage and happiness: Oishi, Kesebir, and Diener (2011)"
+title: "[Re] Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)"
 author: "Lauren Heintz, Tara Wilson, Ben Mathieu, Will Wright"
@@
 
+```{r, echo = FALSE}
+
+myfunction <- function(arg1, arg2){
+  print(seq(arg2))
+  print("hello world")
+}
+
+myfunction(32,44)
+
+```
+
 # Results
@@
 
-# References
+# References Cited
 

### 2020-02-17 analysis/001-creates-table-1.R
Makes script to create table 1 to be read in by paper.Rmd

@@ -1,0 +1,37 @@
+require(car)
+require(Hmisc)
+require(Matrix)
+require(lme4)
+library(xtable)
+library(gssr)
+
+Gini = read.csv("../data/Gini_families.csv")
+data(gss_all)
+happy = gss_all
+happy$Year = happy$year
+happy = merge(happy, Gini, by="Year")
+
+happy$Happiness = recode(happy$happy, "1=3; 3=1; c(0,8,9)=NA")
+happy$TRUSTrecode = recode(happy$trust, "1=3; 2=1; 3=2; c(0,8,9)=NA")
+happy$FAIRrecode = recode(happy$fair, "2=3; 3=2; c(0,8,9)=NA")
+happy$Age = recode(happy$age, "c(9)=NA")
+happy$REALINCrecode = recode(happy$realinc, "0=NA")
+happy$REALINClog = log(happy$REALINCrecode)
+happy$White = as.numeric(happy$race==1)
+happy$Married = as.numeric(happy$marital==1)
+
+origData = happy[happy$Year<=2008,]
+
+#### Table. Correlation of control variables and reported happiness
+income = cor.test(origData$REALINClog, origData$Happiness)
+age = cor.test(origData$Age, origData$Happiness)
+sex = cor.test(origData$sex, origData$Happiness)
+race = cor.test(origData$White, origData$Happiness)
+marital = cor.test(origData$Married, origData$Happiness)
+
+Estimate = round(c(income$estimate,age$estimate,sex$estimate,race$estimate,marital$estimate),3)
+p = round(c(income$p.value,age$p.value,sex$p.value,race$p.value,marital$p.value),3)
+table1 = as.data.frame(cbind(Estimate,p))
+names(table1)[2] = "p value"
+rownames(table1) = c("Logged Income", "Age", "Sex", "White", "Married")
+xtable(table1, caption="Correlations between happiness and control variables")

### 2020-02-17 analysis/paper.Rmd
adding reference to original paper
converted cleaning and visuals to tidyverse

@@
 
-``` {r setup, echo = FALSE}
+``` {r setup, echo = FALSE, message = FALSE, warnings = FALSE}
 knitr::opts_chunk$set(
@@
 #knitr::read_chunk("src/my-external-code.R")
+
+# load packages
+library(tidyverse)
+library(gssr)
 ```
+
+```{r get_data, echo = FALSE}
+# ==== Get Data
+# The happiness, race, and marital data comes from the gssr package and not the provided data since the provided version
+  # does not have race or marital status. For more information, go to https://kjhealy.github.io/gssr/
+data(gss_all)
+
+# The Gini indices come from the provided dataset
+gini <-  read.csv("../data/Gini_families.csv") %>%
+  select(year = Year, gini = Total)
+
+# ==== Clean data
+# Subset the GSS data to just the relevant fields
+gss <- gss_all %>%
+  select(year, happy, race, marital) %>%
+  mutate(year = as.integer(year), # fix data class
+         happy = as.integer(happy),
+         happy = recode(happy, `1`= 3, `2` = 2, `3` = 1), # reverse the values such that higher is more happy
+         race = as.integer(race),
+         marital = as.integer(marital)) %>%
+  na.omit() # remove NAs (4780/64,814 cases where not all data was collected)
+
+# join the gini and happiness/race/marital data
+happy <- gini %>%
+  left_join(gss, by = c("year" = "year")) %>%
+  na.omit()
+
+# create summary table by year
+happy_race_summary <- happy %>%
+  group_by(year, race) %>%
+  summarize(happy_avg = mean(happy))
+
+# write a function
+
+```
+
+```{r plots}
+g <- ggplot(happy_race_summary, aes(x = year, y = happy_avg, color = factor(race)))
+g + geom_point() +
+  geom_line(stat = "smooth",
+            method = "lm", 
+            se = FALSE, 
+            alpha = 0.5) +
+  theme_bw() +
+  labs(title = "Figure 3",
+       x = "Year",
+       y = "Mean Happiness",
+       caption = "Figure 3") +
+  scale_color_discrete(name="Race",
+                      breaks=c(1, 2, 3),
+                      labels=c("White", "Black", "Other")) +
+  scale_y_continuous(limits = c(1.9,2.5))
+
+```
+
+A reference implementation of:
+
+> Grunberg, Rebecca L., Hyejun Kim, and Minjae Kim. 2014a. “Marriage and Happiness Grunberg Kim Kim.pdf.” Harvard Dataverse. https://doi.org/10.7910/DVN/25655/MB980L
+
+Which is a reference implementation of:
+
+> Oishi, S., Kesebir, S., & Diener, E. (2011). Income Inequality and Happiness. Psychological Science, 22(9), 1095–1100. https://doi.org/10.1177/0956797611417262
 
@@
 Reference 2: @data
+Reference 3: @incomeinequality
 

### 2020-02-17 analysis/paper.Rmd
Adds references to the original tables and images into paper.rmd

@@
 
+```{r, table1, fig.cap="Table 1 from the original paper", echo=FALSE}
+knitr::include_graphics("original_paper_table_1.png")
+```
+
+The results from Table 1 in the original paper are shown in Figure \@ref(fig:table1).
+
+```{r, table2, fig.cap="Table 2 from the original paper", echo=FALSE}
+knitr::include_graphics("original_paper_table_2.png")
+```
+
+The results from Table 2 in the original paper are shown in Figure \@ref(fig:table2).
+
 # Conclusion

### 2020-02-17 analysis/001-creates-table-1.R
Removes unnecessary data references

@@ -5,11 +5,8 @@ require(lme4)
 library(xtable)
 library(gssr)
 
-Gini = read.csv("../data/Gini_families.csv")
 data(gss_all)
 happy = gss_all
-happy$Year = happy$year
-happy = merge(happy, Gini, by="Year")
 
 happy$Happiness = recode(happy$happy, "1=3; 3=1; c(0,8,9)=NA")
 happy$TRUSTrecode = recode(happy$trust, "1=3; 2=1; 3=2; c(0,8,9)=NA")
@@ -20,7 +17,7 @@ happy$REALINClog = log(happy$REALINCrecode)
 happy$White = as.numeric(happy$race==1)
 happy$Married = as.numeric(happy$marital==1)
 
-origData = happy[happy$Year<=2008,]
+origData = happy[happy$year<=2008,]
 
 #### Table. Correlation of control variables and reported happiness
 income = cor.test(origData$REALINClog, origData$Happiness)

### 2020-02-19 analysis/paper.Rmd
Started Methods section (brief)

--- 2020-02-16 analysis/paper.Rmd
@@
 
+A reference implementation of:
+
+> Grunberg, Rebecca L., Hyejun Kim, and Minjae Kim. 2014a. “Marriage and Happiness Grunberg Kim Kim.pdf.” Harvard Dataverse. https://doi.org/10.7910/DVN/25655/MB980L
+
+Which is a reference implementation of:
+
+> Oishi, S., Kesebir, S., & Diener, E. (2011). Income Inequality and Happiness. Psychological Science, 22(9), 1095–1100. https://doi.org/10.1177/0956797611417262
+
 # Introduction
@@
 # Methods
+
+The paper of interest[@data] used linear models to show that the correlations drawn by the original findings[@incomeinequality] do not have an effect on the response variable, happiness, by factoring in interactions of variables known correlated variables.
+
+In this replication paper, three artifacts from the original paper[@data] were reproduced.
+The first artifact is "figure 2 (ADD FIGURE 2)..." which plots the mean happiness by year and race.
+The second artifact is table1 which shows the linear regression model's coefficients.
+The third artifact is table2 which shows the muliti correlation coefficients.
+
+## Dataset
+
+Marriage and Happiness[@data], obtained data from the General Social Survey (GSS) and the US Census Bureau.
+The subset of GSS data provided omitted the RACE and MARITAL columns crucial to the replication of the figures and models.
+
+In order to complete the missing data, the original dataset was queried directly using the gssr [add reference here?] R package.
+This new dataset was then merged with the unchanged US Census Bureau data found in gini_..csv.
+
+## Replicating Figure 2 - [INSER FULL FIGURE NAME HERE]
+
+The original R code used the standard R libaries for visualizations. The da
 
@@
 
+## Replicating Table 1
+
+## Replicating Table 2
+
 # Results
 
+We obtained ...
+
 # Conclusion
+
+Replication of this paper was utlimately contingent on tracing back the original dataset.
+Without this resource being cited and publically available, it would not have been possible to replicate the different tables and figure presented in the original paper.
 

### 2020-02-19 analysis/paper.Rmd

--- 2020-02-17 analysis/paper.Rmd
@@
 
+The paper of interest[@data] used linear models to show that the correlations drawn by the original findings[@incomeinequality] do not have an effect on the response variable, happiness, by factoring in interactions of variables known correlated variables.
+
+In this replication paper, three artifacts from the original paper[@data] were reproduced.
+The first artifact is "figure 2 (ADD FIGURE 2)..." which plots the mean happiness by year and race.
+The second artifact is table1 which shows the linear regression model's coefficients.
+The third artifact is table2 which shows the muliti correlation coefficients.
+
+## Dataset
+
+Marriage and Happiness[@data], obtained data from the General Social Survey (GSS) and the US Census Bureau.
+The subset of GSS data provided omitted the RACE and MARITAL columns crucial to the replication of the figures and models.
+
+In order to complete the missing data, the original dataset was queried directly using the gssr [add reference here?] R package.
+This new dataset was then merged with the unchanged US Census Bureau data found in gini_..csv.
+
+## Replicating Figure 2 - [INSER FULL FIGURE NAME HERE]
+
+The original R code used the standard R libaries for visualizations. The da
+
 ```{r, echo = FALSE}
@@
 
+## Replicating Table 1
+
+## Replicating Table 2
+
 # Results
+
+We obtained ...
 
@@
 
+Replication of this paper was utlimately contingent on tracing back the original dataset.
+Without this resource being cited and publically available, it would not have been possible to replicate the different tables and figure presented in the original paper.
+
 # References Cited

### 2020-02-20 analysis/001-creates-table-1.R
Adds sections to the R scripts to be able to execute them in parts in paper.Rmd

@@ -1,34 +1,37 @@
-require(car)
-require(Hmisc)
-require(Matrix)
-require(lme4)
-library(xtable)
-library(gssr)
-
-data(gss_all)
-happy = gss_all
-
-happy$Happiness = recode(happy$happy, "1=3; 3=1; c(0,8,9)=NA")
-happy$TRUSTrecode = recode(happy$trust, "1=3; 2=1; 3=2; c(0,8,9)=NA")
-happy$FAIRrecode = recode(happy$fair, "2=3; 3=2; c(0,8,9)=NA")
-happy$Age = recode(happy$age, "c(9)=NA")
-happy$REALINCrecode = recode(happy$realinc, "0=NA")
-happy$REALINClog = log(happy$REALINCrecode)
-happy$White = as.numeric(happy$race==1)
-happy$Married = as.numeric(happy$marital==1)
-
-origData = happy[happy$year<=2008,]
-
-#### Table. Correlation of control variables and reported happiness
-income = cor.test(origData$REALINClog, origData$Happiness)
-age = cor.test(origData$Age, origData$Happiness)
-sex = cor.test(origData$sex, origData$Happiness)
-race = cor.test(origData$White, origData$Happiness)
-marital = cor.test(origData$Married, origData$Happiness)
-
-Estimate = round(c(income$estimate,age$estimate,sex$estimate,race$estimate,marital$estimate),3)
-p = round(c(income$p.value,age$p.value,sex$p.value,race$p.value,marital$p.value),3)
-table1 = as.data.frame(cbind(Estimate,p))
-names(table1)[2] = "p value"
-rownames(table1) = c("Logged Income", "Age", "Sex", "White", "Married")
-xtable(table1, caption="Correlations between happiness and control variables")
+# ---- import-and-clean-the-data-for-table-1
+  require(car)
+  require(Hmisc)
+  require(Matrix)
+  require(lme4)
+  library(xtable)
+  library(gssr)
+  
+  data(gss_all)
+  happy = gss_all
+  
+  happy$Happiness = recode(happy$happy, "1=3; 3=1; c(0,8,9)=NA")
+  happy$TRUSTrecode = recode(happy$trust, "1=3; 2=1; 3=2; c(0,8,9)=NA")
+  happy$FAIRrecode = recode(happy$fair, "2=3; 3=2; c(0,8,9)=NA")
+  happy$Age = recode(happy$age, "c(9)=NA")
+  happy$REALINCrecode = recode(happy$realinc, "0=NA")
[…]

### 2020-02-20 analysis/002-creates-table-2.R

@@ -1,44 +1,46 @@
-rm(list=ls())
-require(car)
-require(Hmisc)
-require(Matrix)
-require(lme4)
-library(xtable)
-library(gssr)
-library(stargazer)
+# ---- import-and-clean-the-data-for-table-2
+  require(car)
+  require(Hmisc)
+  require(Matrix)
+  require(lme4)
+  library(xtable)
+  library(gssr)
+  library(stargazer)
+  
+  Gini = read.csv("../data/Gini_families.csv")
+  data(gss_all)
+  happy = gss_all
+  happy$Year = happy$year
+  happy = merge(happy, Gini, by="Year")
+  
+  happy$Happiness = recode(happy$happy, "1=3; 3=1; c(0,8,9)=NA")
+  happy$Age = recode(happy$age, "c(9)=NA")
+  happy$REALINCrecode = recode(happy$realinc, "0=NA")
+  happy$REALINClog = log(happy$REALINCrecode)
+  happy$White = as.numeric(happy$race==1)
+  happy$Married = as.numeric(happy$marital==1)
+  happy$Gini = happy$Total
 
-Gini = read.csv("../data/Gini_families.csv")
-data(gss_all)
-happy = gss_all
-happy$Year = happy$year
-happy = merge(happy, Gini, by="Year")
+  origData = happy[happy$Year<=2008,]
+  
+# ---- run-the-regressions
+  m1 = lmer(Happiness ~ Gini + (1 | Year), data=origData)
+  ci.m1 = confint(m1)
+  
+  m2 = lmer(Happiness ~ Gini + REALINClog + (1 | Year), data=origData)
+  m2.ci = confint(m2)
+  
+  m3 = lmer(Happiness ~ Gini + Age + (1 | Year), data=origData)
+  m3.ci = confint(m3)
+  
+  m4 = lmer(Happiness ~ Gini + factor(sex) + (1 | Year), data=origData)
+  m4.ci = confint(m4)
+  
+  m5 = lmer(Happiness ~ Gini + White + (1 | Year), data=origData)
+  m5.ci = confint(m5)
+  
+  m6 = lmer(Happiness ~ Gini + Married + (1 | Year), data=origData)
+  m6.ci = confint(m6)
 
-happy$Happiness = recode(happy$happy, "1=3; 3=1; c(0,8,9)=NA")
-happy$Age = recode(happy$age, "c(9)=NA")
[…]

### 2020-02-20 analysis/paper.Rmd
Adds read in for table 1 R script

--- 2020-02-17 analysis/paper.Rmd
@@
   fig.path = "../figures")
-#knitr::read_chunk("src/my-external-code.R")
+
+knitr::read_chunk("001-creates-table-1.R")
+knitr::read_chunk("002-creates-table-2.R")
 
@@
 
+```{r import-and-clean-the-data-for-table-1, eval=TRUE}
+```
+
+```{r create-the-correlations-and-table, eval=TRUE}
+```
+
+```{r display-table-1, eval=TRUE, results='asis'}
+```
+
 ```{r, table1, fig.cap="Table 1 from the original paper", echo=FALSE}

### 2020-02-20 analysis/paper.Rmd
metadata.yaml replaced, abstract added to report and yaml

@@
 ```
+
+A reference implementation of:
+
+> Grunberg, Rebecca L., Hyejun Kim, and Minjae Kim. 2014a. “Marriage and Happiness Grunberg Kim Kim.pdf.” Harvard Dataverse. https://doi.org/10.7910/DVN/25655/MB980L
+
+Which is a reference implementation of:
+
+> Oishi, S., Kesebir, S., & Diener, E. (2011). Income Inequality and Happiness. Psychological Science, 22(9), 1095–1100. https://doi.org/10.1177/0956797611417262
+
+The purpose of the following paper is to do a replication of the paper "Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)" [@marriagehappiness].
+There is a crisis of reproducibility and replication in data science field.
+This paper follows the ReScience method of replicating a research paper to further validate the results of the paper.
+This particular replication is unique, because the paper being replicated is actually an alternate implementation of another paper, "Income Inequality and Happiness" [@incomeinequality].
+While the first paper draws a connection between happiness and income, the second paper calls in the question the data used for this conclusion, and pulls in additional data for analysis.
+This second analysis, focused more on marriage and happiness is what this paper seeks to replicate.
+
+# Introduction
 
@@
 
-A reference implementation of:
-
-> Grunberg, Rebecca L., Hyejun Kim, and Minjae Kim. 2014a. “Marriage and Happiness Grunberg Kim Kim.pdf.” Harvard Dataverse. https://doi.org/10.7910/DVN/25655/MB980L
-
-Which is a reference implementation of:
-
-> Oishi, S., Kesebir, S., & Diener, E. (2011). Income Inequality and Happiness. Psychological Science, 22(9), 1095–1100. https://doi.org/10.1177/0956797611417262
-
-# Introduction
-
 # Methods

### 2020-02-21 analysis/paper.Rmd
corrected fig3 issues and both replicated and reproduced it

@@
 # ==== Clean data
-# Subset the GSS data to just the relevant fields
-gss <- gss_all %>%
+# Subset the GSS data to just the relevant fields for the relevant time frame, join, and recode the same way the 
+  # original study does
+study_data <- gss_all  %>%
   select(year, happy, race, marital) %>%
-  mutate(year = as.integer(year), # fix data class
-         happy = as.integer(happy),
-         happy = recode(happy, `1`= 3, `2` = 2, `3` = 1), # reverse the values such that higher is more happy
-         race = as.integer(race),
-         marital = as.integer(marital)) %>%
-  na.omit() # remove NAs (4780/64,814 cases where not all data was collected)
+  filter(year <= 2012) %>%
+  mutate(year = as.integer(year),
+         happy = dplyr::recode(happy, `1`= 3L, `2` = 2L, `3` = 1L)) %>% #recode to increasing happiness from 1 to 3
+  left_join(gini, by = c("year" = "year"))
 
-# join the gini and happiness/race/marital data
-happy <- gini %>%
-  left_join(gss, by = c("year" = "year")) %>%
-  na.omit()
+# Relabel the labels attribute to reflect the inverse of the happiness intensity (not actually used, but prolly good)
+attributes(study_data$happy)$labels <- c("NOT TOO HAPPY" = 1, "PRETTY HAPPY" = 2, "VERY HAPPY" = 3)
 
-# create summary table by year
-happy_race_summary <- happy %>%
+# Create summary table of mean happiness by year by race
+race_summary <- study_data %>%
   group_by(year, race) %>%
-  summarize(happy_avg = mean(happy))
+  dplyr::summarize(happy_avg = mean(na.omit(happy))) # we can remove the 'dplyr' once we only have the tidyverse loaded
 
@@
 ```{r plots}
-g <- ggplot(happy_race_summary, aes(x = year, y = happy_avg, color = factor(race)))
-g + geom_point() +
+
+# Fig 3 reproduction
+g <- ggplot(race_summary, aes(x = year, y = happy_avg, color = factor(race)))
+g + geom_point(size = .6) +
   geom_line(stat = "smooth",
@@
   theme_bw() +
-  labs(title = "Figure 3",
+  labs(title = "Average Happiness by Race Trend",
        x = "Year",
@@
        caption = "Figure 3") +
-  scale_color_discrete(name="Race",
+  scale_color_manual(values=c("blue", "forestgreen", "dodgerblue"),
+                     name="Race",
                      breaks=c(1, 2, 3),
                      labels=c("White", "Black", "Other")) +
-  scale_y_continuous(limits = c(1.9,2.5))
+  coord_cartesian(ylim = c(1.9,2.5)) # setting this to match the study excludes the lm via the above methodology
 

### 2020-02-21 analysis/001-creates-table-1.R
Updates table output from latex to html

@@ -3,9 +3,9 @@
   require(Hmisc)
   require(Matrix)
   require(lme4)
-  library(xtable)
   library(gssr)
-  
+  library(xtable)
+
   data(gss_all)
   happy = gss_all
   
@@ -34,4 +34,4 @@
   rownames(table1) = c("Logged Income", "Age", "Sex", "White", "Married")
   
 # ---- display-table-1
-  print(xtable(x=table1), type="latex", comment=FALSE)
+  print(xtable(x=table1), type="html", comment=FALSE)

### 2020-02-21 analysis/002-creates-table-2.R
Updates path for Gini data to be relative to main repo

@@ -7,7 +7,7 @@
   library(gssr)
   library(stargazer)
   
-  Gini = read.csv("../data/Gini_families.csv")
+  Gini = read.csv("data/Gini_families.csv")
   data(gss_all)
   happy = gss_all
   happy$Year = happy$year
@@ -44,3 +44,5 @@
 
 # ---- display-table-2
   stargazer(m1,m2,m3,m4,m5,m6)
+
+  

### 2020-02-21 analysis/paper.Rmd
Adds second table and comparison to tables in original paper

@@
 
-The results from Table 1 in the original paper are shown in Figure \@ref(fig:table1).
+We were table to almost exactly reproduce the results from Table 1 in the original paper that shown in Figure \@ref(fig:table1).
+The only difference is the estimate for Sex was 0.01 in the publication compared to 0.00 in our replication.
+This may be due to rounding versions or an underlying exclusion of outliers we saw with the above plot.
+
+```{r import-and-clean-the-data-for-table-2, eval=TRUE}
+```
+
+```{r run-the-regressions, eval=TRUE}
+```
+
+```{r display-table-2, eval=TRUE, results='asis'}
+```
 
@@
 
-The results from Table 2 in the original paper are shown in Figure \@ref(fig:table2).
+Again we were able to almost identically reproduce the results from Table 2 in the original paper, shown in Figure \@ref(fig:table2).
+Aside from slight variability in the second and third decimal places, our results from the linear models are very close.
+There are several differences wit the number of observations, listed in the bottom of the table, which is to be expected as we are using a package with the GSS data and it is likely not an identical snapshot to the one used in the original paper.
+Overall though these two tables were indeed highly reproducible even with different input data.
 

### 2020-02-22 analysis/paper.Rmd

@@
   mutate(year = as.integer(year),
-         happy = dplyr::recode(happy, `1`= 3L, `2` = 2L, `3` = 1L)) %>% #recode to increasing happiness from 1 to 3
+         happy = dplyr::recode(as.integer(happy), `1`= 3L, `2` = 2L, `3` = 1L)) %>% #recode to increasing happiness from 1 to 3
   left_join(gini, by = c("year" = "year"))
@@
 ```
+
+## Replicating Table 1
+
+## Replicating Table 2
 

### 2020-02-22 analysis/paper.Rmd
Fixed typos in the introduction

@@
 The purpose of the following paper is to do a replication of the paper "Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)" [@marriagehappiness].
-There is a crisis of reproducibility and replication in data science field.
-This paper follows the ReScience method of replicating a research paper to further validate the results of the paper.
-This particular replication is unique, because the paper being replicated is actually an alternate implementation of another paper, "Income Inequality and Happiness" [@incomeinequality].
+There is a crisis of reproducibility and replication in the data science field.
+This paper follows the ReScience method[TODO ADD REFERENCE HERE] of replicating a research paper to further validate the results of the paper.
+This particular replication is unique, because the paper being replicated is an alternate implementation of another paper:"Income Inequality and Happiness" [@incomeinequality].
 While the first paper draws a connection between happiness and income, the second paper calls in the question the data used for this conclusion, and pulls in additional data for analysis.
-This second analysis, focused more on marriage and happiness is what this paper seeks to replicate.
+This second analysis, focused on the relationship between marriage and happiness which is what the current paper seeks to replicate.
 

### 2020-02-22 analysis/paper.Rmd
Updated with improvements to introduction and additions to the Methods section

@@
 
-The purpose of the following paper is to do a replication of the paper "Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)" [@marriagehappiness].
 There is a crisis of reproducibility and replication in the data science field.
-This paper follows the ReScience method[TODO ADD REFERENCE HERE] of replicating a research paper to further validate the results of the paper.
-This particular replication is unique, because the paper being replicated is an alternate implementation of another paper:"Income Inequality and Happiness" [@incomeinequality].
-While the first paper draws a connection between happiness and income, the second paper calls in the question the data used for this conclusion, and pulls in additional data for analysis.
-This second analysis, focused on the relationship between marriage and happiness which is what the current paper seeks to replicate.
+In an attempt to bolster confidence in scientific results, the following paper is a replication of "Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)" [@marriagehappiness].
+This paper follows the ReScience replication method[@rescience] which strongly encourages open source practices as underlined by the format of this project: a github compendium.
+This particular replication is unique in that the paper being replicated is an alternate implementation of the paper:"Income Inequality and Happiness" [@incomeinequality].
+While the first paper draws a connection between happiness and income, the second calls in the question the data used for this conclusion, and pulls in additional data for analysis.
+This second analysis, focused on the relationship between marriage and happiness, is the subject of replication in this paper.
 
@@
 
+# Methods
+
+## Overview
+
+The paper of interest[@data] used linear models to show that the correlations drawn by the original findings[@incomeinequality] do not hold once the interactions of variables known to be correlated with the response variables are added to the model.
+
+In this replication paper, three artifacts from the paper[@data] were reproduced.
+The first artifact, Figure 3., plots the mean happiness by year and race, the second, Table 1, shows the linear regression model's coefficients and the third, Table 2, shows the correlation coefficients of the different independent variables used in the linear models created.
+
+## Dataset
+
+Marriage and Happiness[@data], obtained data from the General Social Survey (GSS) and the US Census Bureau.
+The subset of GSS data provided omitted the RACE and MARITAL columns crucial to the replication of the figures and models.
+In order to complete the missing data, the original dataset was queried directly using the gssr[@gssr] R package.
+
+The dataset from gssr contained a larger time interval than the original paper, it was filtered back to match the original intervals.
+This dataset was also merged with the original US Census Bureau data found in Gini_families.csv[@data] by appending the total column to the GSS data using year as the key.
+The "happy" variable was re-encoded so that the numerical factor would reflect an increasing level of happiness as per the original code.
+
+## Replicating Figure 3
+
+```{r, figure3, fig.cap="Figure 3 from the original paper", echo=FALSE}
+knitr::include_graphics("original_paper_figure_3.png")
+```
+
+The original R code used the standard R libraries for visualizations.
+The ggplot2 package was leveraged to replicate the figure with the new dataset.
+Axis labels, lines and colors were adjusted to match the original output.
+
+## Replicating Table 1
+
+```{r, table1, fig.cap="Table 1 from the original paper", echo=FALSE}
+knitr::include_graphics("original_paper_table_1.png")
+```
+
+The R function cor.test() was used to get the Pearson correlation coefficient between the different independent variables (income, age, sex, white, married) and happiness.
+Grundberg et al.'s code was slightly modified to keep the same encoding of variables given the new dataset input.
+
+## Replicating Table 2
+
+```{r, table2, fig.cap="Table 2 from the original paper", echo=FALSE}
+knitr::include_graphics("original_paper_table_2.png")
+```
+
+Grundberg et al used the lme4 package to generate coefficients of linear mixed-effects models using the intercept to capture year as the random effect (see [@lmefour] section 2).
+
+# Results
+
 ```{r plots}
-
 # Fig 3 reproduction
@@
   coord_cartesian(ylim = c(1.9,2.5)) # setting this to match the study excludes the lm via the above methodology
-
 ```
-
-# Methods
-
-The paper of interest[@data] used linear models to show that the correlations drawn by the original findings[@incomeinequality] do not have an effect on the response variable, happiness, by factoring in interactions of variables known correlated variables.
-
-In this replication paper, three artifacts from the original paper[@data] were reproduced.
-The first artifact is "figure 2 (ADD FIGURE 2)..." which plots the mean happiness by year and race.
-The second artifact is table1 which shows the linear regression model's coefficients.
-The third artifact is table2 which shows the muliti correlation coefficients.
-
-## Dataset
-
-Marriage and Happiness[@data], obtained data from the General Social Survey (GSS) and the US Census Bureau.
-The subset of GSS data provided omitted the RACE and MARITAL columns crucial to the replication of the figures and models.
-
-In order to complete the missing data, the original dataset was queried directly using the gssr [add reference here?] R package.
-This new dataset was then merged with the unchanged US Census Bureau data found in gini_..csv.
-
-## Replicating Figure 2 - [INSER FULL FIGURE NAME HERE]
-
-The original R code used the standard R libaries for visualizations. The da
-
-```{r, echo = FALSE}
-
-myfunction <- function(arg1, arg2){
-  print(seq(arg2))
-  print("hello world")
-}
-
-myfunction(32,44)
-
-```
-
-## Replicating Table 1
-
-## Replicating Table 2
-
-# Results
 
@@
 
-```{r, table1, fig.cap="Table 1 from the original paper", echo=FALSE}
-knitr::include_graphics("original_paper_table_1.png")
-```
-
-We were table to almost exactly reproduce the results from Table 1 in the original paper that shown in Figure \@ref(fig:table1).
+The  to almost exactly reproduce the results from Table 1 in the original paper that shown in Figure \@ref(fig:table1).
 The only difference is the estimate for Sex was 0.01 in the publication compared to 0.00 in our replication.
@@
 
-```{r, table2, fig.cap="Table 2 from the original paper", echo=FALSE}
-knitr::include_graphics("original_paper_table_2.png")
-```
-
 Again we were able to almost identically reproduce the results from Table 2 in the original paper, shown in Figure \@ref(fig:table2).
@@
 
-Replication of this paper was utlimately contingent on tracing back the original dataset.
-Without this resource being cited and publically available, it would not have been possible to replicate the different tables and figure presented in the original paper.
+Replication of this paper was ultimately contingent on tracing back the original dataset.
+Without this resource being cited and publicly available, it would not have been possible to replicate the different tables and figure presented in the original paper.
 
@@
 Reference 3: @incomeinequality  
+Reference 4: @gssr  
+Reference 5: @rescience  
+Reference 6: @lmefour
 

### 2020-02-22 analysis/paper.Rmd
Fixed typos, added missing figure.

@@
 This particular replication is unique in that the paper being replicated is an alternate implementation of the paper:"Income Inequality and Happiness" [@incomeinequality].
-While the first paper draws a connection between happiness and income, the second calls in the question the data used for this conclusion, and pulls in additional data for analysis.
-This second analysis, focused on the relationship between marriage and happiness, is the subject of replication in this paper.
+While the first paper draws a connection between happiness and income, the second calls into question the data used to obtain the results stated, and pulls in additional data to re-assess the analysis.
+This second analysis, which focused on the relationship between marriage and happiness, is the subject of replication in this paper.
 
@@
 
-In this replication paper, three artifacts from the paper[@data] were reproduced.
+In this replication paper, three artifacts from [@data] were reproduced.
 The first artifact, Figure 3., plots the mean happiness by year and race, the second, Table 1, shows the linear regression model's coefficients and the third, Table 2, shows the correlation coefficients of the different independent variables used in the linear models created.
@@
 
-The R function cor.test() was used to get the Pearson correlation coefficient between the different independent variables (income, age, sex, white, married) and happiness.
+The R function cor.test() was used to get the Pearson correlation coefficient between the different independent variables (income, age, sex, white, married) and the response variable, happiness.
 Grundberg et al.'s code was slightly modified to keep the same encoding of variables given the new dataset input.

### 2020-02-23 analysis/001-creates-table-1.R
Outputs table 1 as image to allow inclusion into Rmd

@@ -4,8 +4,8 @@
   require(Matrix)
   require(lme4)
   library(gssr)
-  library(xtable)
-
+  library(kableExtra)
+  
   data(gss_all)
   happy = gss_all
   
@@ -19,7 +19,7 @@
   happy$Married = as.numeric(happy$marital==1)
   
   origData = happy[happy$year<=2008,]
-  
+
 # ---- create-the-correlations-and-table
   income = cor.test(origData$REALINClog, origData$Happiness)
   age = cor.test(origData$Age, origData$Happiness)
@@ -32,6 +32,9 @@
   table1 = as.data.frame(cbind(Estimate,p))
   names(table1)[2] = "p value"
   rownames(table1) = c("Logged Income", "Age", "Sex", "White", "Married")
-  
+
 # ---- display-table-1
-  print(xtable(x=table1), type="html", comment=FALSE)
+  knitr::kable(x=table1, "html", booktabs = TRUE, linesep = "") %>% 
+    kable_styling(full_width = TRUE, font_size = 12) %>% 
+    column_spec(1, width = "4cm") %>% 
+    save_kable(file = "table_1.png")

### 2020-02-23 analysis/replication-tara.R
Removes images and scripts we no longer need

@@ -1,216 +1,0 @@
-#### GOV2001 REPLICATION CODE ####
-## Replication of "Inequality and Happiness" ##
-## (Oishi, Kesebir, & Diener, 2011) ##
-## Rebecca Grunberg, Hyejun Kim, & Minjae Kim ##
-## May 2014 ##
-## Replication data available at Harvard Dataverse ##
-
-rm(list=ls())
-require(car)
-require(Hmisc)
-require(Matrix)
-require(lme4)
-library(xtable)
-require(stargazer)
-
-# load the data
-Gini = read.csv("../data/Gini_families.csv")
-happy = read.table("../data/sub-data.txt", header=T, sep=",")
-names(happy)[5] = "Year"
-happy = merge(happy, Gini, by="Year")
-
-# recode the GSS variables
-happy$Happiness = recode(happy$HAPPY, "1=3; 3=1; c(0,8,9)=NA")
-happy$TRUSTrecode = recode(happy$TRUST, "1=3; 2=1; 3=2; c(0,8,9)=NA")
-happy$FAIRrecode = recode(happy$FAIR, "2=3; 3=2; c(0,8,9)=NA")
-happy$Age = recode(happy$AGE, "c(9)=NA")
-happy$REALINCrecode = recode(happy$REALINC, "0=NA")
-happy$REALINClog = log(happy$REALINCrecode)
-happy$White = as.numeric(happy$NATRACE==1)
-#happy$Married = as.numeric(happy$MARITAL==1)
-happy$Gini = happy$Total
-
-# create two data sets, one for original data used in the paper (through 2008)
-# and another for the full data set (now available through 2012)
-origData = happy[happy$Year<=2008,]
-fullData = happy
-
-#### replicate multilevel model, Gini and happiness: Model 1
-m1 = lmer(Happiness ~ Gini + (1 | Year), data=origData)
-summary(m1)
-ci.m1 = confint(m1)
-
-#### RESPONDENT'S RACE ####
-# race is correlated with happiness, see correlation table
-# AND there are significant shifts in race, see figure of demographic trends
-#### Figures 2 and 3. plot of proportion white x mean happiness, happiness of racial groups
-happyByYear = aggregate(Happiness ~ Year, FUN=mean, data=origData)
-
-#### Figure 1. Pattern over time of inequality, race, marital status
-png(file='Figure1.png', units='in', width=11, height=8.5, res=400)
-par(mfrow=c(2,2))
-#inequality
[…]

### 2020-02-23 analysis/001-creates-table-1.R
Takes out unused recodings

@@ -10,8 +10,6 @@
   happy = gss_all
   
   happy$Happiness = recode(happy$happy, "1=3; 3=1; c(0,8,9)=NA")
-  happy$TRUSTrecode = recode(happy$trust, "1=3; 2=1; 3=2; c(0,8,9)=NA")
-  happy$FAIRrecode = recode(happy$fair, "2=3; 3=2; c(0,8,9)=NA")
   happy$Age = recode(happy$age, "c(9)=NA")
   happy$REALINCrecode = recode(happy$realinc, "0=NA")
   happy$REALINClog = log(happy$REALINCrecode)

### 2020-02-23 analysis/001-creates-table-1.R
Updates kable styling to not use full width for table 1 formatting

@@ -33,6 +33,6 @@
 
 # ---- display-table-1
   knitr::kable(x=table1, "html", booktabs = TRUE, linesep = "") %>% 
-    kable_styling(full_width = TRUE, font_size = 12) %>% 
+    kable_styling(full_width = FALSE, font_size = 12) %>% 
     column_spec(1, width = "4cm") %>% 
     save_kable(file = "table_1.png")

### 2020-02-23 analysis/002-creates-table-2.R
Updates table 2 to save to png file as output

@@ -6,6 +6,7 @@
   library(xtable)
   library(gssr)
   library(stargazer)
+  library(kableExtra)
   
   Gini = read.csv("../data/Gini_families.csv")
   data(gss_all)
@@ -43,6 +44,11 @@
   m6.ci = confint(m6)
 
 # ---- display-table-2
-  stargazer(m1,m2,m3,m4,m5,m6)
+  output <- stargazer(m1,m2,m3,m4,m5,m6, type="text")
+  
+  knitr::kable(x=output, "html", booktabs = TRUE, linesep = "&&") %>% 
+    kable_styling(full_width = FALSE, font_size = 12) %>% 
+    column_spec(1, width = "4cm") %>% 
+    save_kable(file = "table_2.png")
 
   

### 2020-02-23 analysis/paper.Rmd
Adds details for table 1 and table 2 replication process, also adds details to conclusion/intro

@@
 
-There is a crisis of reproducibility and replication in the data science field.
-In an attempt to bolster confidence in scientific results, the following paper is a replication of "Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)" [@marriagehappiness].
-This paper follows the ReScience replication method[@rescience] which strongly encourages open source practices as underlined by the format of this project: a github compendium.
-This particular replication is unique in that the paper being replicated is an alternate implementation of the paper:"Income Inequality and Happiness" [@incomeinequality].
-While the first paper draws a connection between happiness and income, the second calls into question the data used to obtain the results stated, and pulls in additional data to re-assess the analysis.
-This second analysis, which focused on the relationship between marriage and happiness, is the subject of replication in this paper.
-
 # Introduction
@@
 
+There is a crisis of reproducibility and replication in the data science field.
+In an attempt to bolster confidence in scientific results, the following paper is a replication of "Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)" [@marriagehappiness].
+This paper follows the ReScience replication method[@rescience] which strongly encourages open source practices as underlined by the format of this project: a github compendium.
+This particular replication is unique in that the paper being replicated is an alternate implementation of the paper:"Income Inequality and Happiness" [@incomeinequality].
+While the first paper draws a connection between happiness and income, the second calls into question the data used to obtain the results stated, and pulls in additional data to re-assess the analysis.
+This second analysis, which focused on the relationship between marriage and happiness, is the subject of replication in this paper.
+
 # Methods
@@
 The dataset from gssr contained a larger time interval than the original paper, it was filtered back to match the original intervals.
+Only years prior to 2008 are used in both analyses.
 This dataset was also merged with the original US Census Bureau data found in Gini_families.csv[@data] by appending the total column to the GSS data using year as the key.
-The "happy" variable was re-encoded so that the numerical factor would reflect an increasing level of happiness as per the original code.
 
-## Replicating Figure 3
+Several encodings for the data were updated in the original paper which were replicated in order to allow accurate comparisons.
+The "happy" variable was re-encoded in a reversed scheme so that the numerical factor would reflect an increasing level of happiness.
+The income data was re-encoded on a log scale.
+Race was encoded numerically where "White" was set to 1.
+The "married" variable was also set to numeric encodings with married respondents denoted by those answering 1.
 
-```{r, figure3, fig.cap="Figure 3 from the original paper", echo=FALSE}
-knitr::include_graphics("original_paper_figure_3.png")
-```
+## Alterations
 
-The original R code used the standard R libraries for visualizations.
-The ggplot2 package was leveraged to replicate the figure with the new dataset.
-Axis labels, lines and colors were adjusted to match the original output.
-
-## Replicating Table 1
-
-```{r, table1, fig.cap="Table 1 from the original paper", echo=FALSE}
-knitr::include_graphics("original_paper_table_1.png")
-```
-
-The R function cor.test() was used to get the Pearson correlation coefficient between the different independent variables (income, age, sex, white, married) and the response variable, happiness.
-Grundberg et al.'s code was slightly modified to keep the same encoding of variables given the new dataset input.
-
-## Replicating Table 2
-
-```{r, table2, fig.cap="Table 2 from the original paper", echo=FALSE}
-knitr::include_graphics("original_paper_table_2.png")
-```
-
-Grundberg et al used the lme4 package to generate coefficients of linear mixed-effects models using the intercept to capture year as the random effect (see [@lmefour] section 2).
+Aside from gathering the input data from a new source, several different packages were used in addition to ensure the reproduced results were adequately tested.
+These will be discussed further in the respective sections below.
 
@@
 
+## Replicating Figure 3
+
+Figure 3 in the original publication plots mean happiness of respondentsover time.
+This data is categorized into 3 groups by racial identity: White, Black and Other.
+Best-fitting regression lines are included to display the trend of mean happiness for the 3 populations.
+
+```{r, figure3, fig.cap="Figure 3 from the original paper", echo=FALSE}
+knitr::include_graphics("original_paper_figure_3.png")
+```
+
+The original R code used the standard R libraries for visualizations.
+The ggplot2 package was leveraged to replicate the figure with the new dataset.
+Axis labels, lines and colors were adjusted to match the original output.
+
+## Replicating Table 1
+
+Table 1 in the original publication explores the correlations between happiness and various control variables found in the dataset.
+
+```{r, table1, fig.cap="Table 1 from the original paper", echo=FALSE}
+knitr::include_graphics("original_paper_table_1.png")
+```
+
+The R function cor.test() was used to get the Pearson correlation coefficient between the different independent variables (income on a log scale, age, sex, white, married) and the response variable, happiness.
+Grundberg et al.'s code was slightly modified to keep the same encoding of variables given the new dataset input.
+
 ```{r import-and-clean-the-data-for-table-1, eval=TRUE}
@@
 
-The  to almost exactly reproduce the results from Table 1 in the original paper that shown in Figure \@ref(fig:table1).
+```{r, table1-replication, fig.cap="Replication of Table 1", echo=FALSE}
+knitr::include_graphics("table_1.png")
+```
+
+We were able to almost exactly reproduce the results from Table 1 in the original paper that shown in Figure \@ref(fig:table1).
 The only difference is the estimate for Sex was 0.01 in the publication compared to 0.00 in our replication.
 This may be due to rounding versions or an underlying exclusion of outliers we saw with the above plot.
+
+The steps taken to reproduce this table are identical to those in the original publication aside from a new input dataset and the use of a combination of the kableExtra and xtable R packages to produce the output compared with xtable alone used in the original publication.
+
+## Replicating Table 2
+
+Table 2 in the original publication explores the output of various linear models on the dependent variable, happiness.
+This is central to the message of the paper and was therefore critical to investigate.
+
+```{r, table2, fig.cap="Table 2 from the original paper", echo=FALSE}
+knitr::include_graphics("original_paper_table_2.png")
+```
+
+Grundberg et al used the lme4 package to generate coefficients of linear mixed-effects models using the intercept to capture year as the random effect (see [@lmefour] section 2).
 
@@
 
+```{r, table2-replication, fig.cap="Replication of Table 2", echo=FALSE}
+knitr::include_graphics("table_2.png")
+```
+
 Again we were able to almost identically reproduce the results from Table 2 in the original paper, shown in Figure \@ref(fig:table2).
 Aside from slight variability in the second and third decimal places, our results from the linear models are very close.
-There are several differences wit the number of observations, listed in the bottom of the table, which is to be expected as we are using a package with the GSS data and it is likely not an identical snapshot to the one used in the original paper.
-Overall though these two tables were indeed highly reproducible even with different input data.
+There are several differences with the number of observations, listed in the bottom of the table, which is to be expected as we are using a package with the GSS data and it is likely not an identical snapshot to the one used in the original paper.
+However, this variability is minor in scale.Even though slight variabilities were observed in different cells throughout this table, no disparities were large enough to impact the significance of the results as denoted in the tables with asterisks.
+Therefore, even with new data sources we found that the conclusions hold for the linear model analysis.
+
+Again, the steps taken to reproduce this table were nearly identical as the original paper aside from a new dataset source and the use of the kable and stargazer packages to produce the output as opposed to strictly stargazer LaTeX table results.
 
@@
 Without this resource being cited and publicly available, it would not have been possible to replicate the different tables and figure presented in the original paper.
+The lack of necessary information included in the published data provided for replication is something that should likely be addressed by the authors as this was a major deterrent to the goal of reproducibility.
+
+Under conditions of both a new source dataset and different R packages used for data manipulation and visualization, the 3 exhibits in the original publication were able to be replicated.
+With only minor discrepancies in the numbers themselves, the conclusions drawn from the paper's graphics were not significantly altered by any means.
+Successful replication of this paper is largely a result of transparency in the original publication providing clarity around data encoding and the models used for analysis.
+This provided a platform upon which we were able to adapt the code and generate results that in large part align directly with those in the publication.
 

### 2020-02-24 analysis/paper.Rmd
Updated rmd

@@
 In this replication paper, three artifacts from [@data] were reproduced.
-The first artifact, Figure 3., plots the mean happiness by year and race, the second, Table 1, shows the linear regression model's coefficients and the third, Table 2, shows the correlation coefficients of the different independent variables used in the linear models created.
+The first artifact, Figure 3., plots the mean happiness by year and race, the second, Table 1, shows the linear regression model's coefficients and the third, Table 2, shows the correlation coefficients of the different independent variables used in the linear mixed-effect models created.
 
@@
 
-The dataset from gssr contained a larger time interval than the original paper, it was filtered back to match the original intervals.
+The dataset from gssr contained a larger time interval than the original paper.
+It was filtered back to match the original interval.
 Only years prior to 2008 are used in both analyses.
-This dataset was also merged with the original US Census Bureau data found in Gini_families.csv[@data] by appending the total column to the GSS data using year as the key.
+This dataset was also merged with the original US Census Bureau data found in Gini_families.csv[@data] by appending the "total" column to the GSS data using "year" as the join key.
 
@@
 
-Figure 3 in the original publication plots mean happiness of respondentsover time.
+Figure 3 in the original publication plots mean happiness of respondents over time.
 This data is categorized into 3 groups by racial identity: White, Black and Other.

### 2020-02-24 analysis/paper.Rmd
intro added

--- 2020-02-23 analysis/paper.Rmd
@@
 
+The purpose of the following paper is to do a replication of the paper "Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)" [@marriagehappiness].
+There is a crisis of reproducibility and replication in data science field.
+This paper follows the ReScience method of replicating a research paper to further validate the results of the paper.
+This particular replication is unique, because the paper being replicated is actually an alternate implementation of another paper, "Income Inequality and Happiness" [@incomeinequality].
+While the first paper draws a connection between happiness and income, the second paper calls in the question the data used for this conclusion, and pulls in additional data for analysis.
+This second analysis, focused more on marriage and happiness is what this paper seeks to replicate.
+
 # Introduction
+
+In the spirit of reproducible science, the team has set out to replicate the paper "Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)" [@marriagehappiness] according to the ReScience standards.
+ReScience defines replication as "a scientific study (computational or other) means repeating a published protocol, respecting its spirit and intentions but varying the technical details.
+For computational work, this would mean using different software, running a simulation from different initial conditions, etc.
+The idea is to change something that everyone believes shouldn’t matter, and see if the scientific conclusions are affected or not" [@rescience].
+
+This replication is unique because it is actually a replication of a replication.
+The first paper, "Income Inequality and Happiness" [@incomeinequality], is a study on happiness and it specifically focuses on income equality.
+The study makes the conclusion that in years where there is greater income inqueality in America, people are less happy.
+The paper attributes this negative relationship to meta variables such as perceived trust and perceived fairness in society.
+The second paper [@marriagehappiness] calls in to question the data and the conclusions used by this study.
+The second paper seeks to do a replication but factor in additionaal data like race, gender, and marriage to test for possible confounding variables.
+Most noteably, a relationship between someone marital status (single vs married) ends up being the only significant factor in a linear regression using all variables.
+In essence, the second paper makes the claim that when controlling for marriage, there is no relationship between income inequality and happiness of Americans - contradicting the first paper.
+
+This paper will now be a third replication, focused on critiquing the methods and traceability of the second paper.
+Throughout the analysis, there are some critical pieces of missing data which led to challenges in even reproducing the results.
+In the effort to reproduce the results, we had to find our own data and sources to tie in for the analysis, making this paper a replication after all.
 
@@
 ```
-
-There is a crisis of reproducibility and replication in the data science field.
-In an attempt to bolster confidence in scientific results, the following paper is a replication of "Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)" [@marriagehappiness].
-This paper follows the ReScience replication method[@rescience] which strongly encourages open source practices as underlined by the format of this project: a github compendium.
-This particular replication is unique in that the paper being replicated is an alternate implementation of the paper:"Income Inequality and Happiness" [@incomeinequality].
-While the first paper draws a connection between happiness and income, the second calls into question the data used to obtain the results stated, and pulls in additional data to re-assess the analysis.
-This second analysis, which focused on the relationship between marriage and happiness, is the subject of replication in this paper.
 

### 2020-02-24 analysis/paper.Rmd
Fixed typos in paper.

--- 2020-02-24 analysis/paper.Rmd
@@
 
+There is a crisis of reproducibility and replication in the data science field.
+In an attempt to bolster confidence in scientific results, the following paper is a replication of "Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)" [@marriagehappiness].
+This paper follows the ReScience replication method[@rescience] which strongly encourages open source practices as underlined by the format of this project: a github compendium.
+This particular replication is unique in that the paper being replicated is an alternate implementation of the paper:"Income Inequality and Happiness" [@incomeinequality].
+While the first paper draws a connection between happiness and income, the second calls into question the data used to obtain the results stated, and pulls in additional data to re-assess the analysis.
+This second analysis, which focused on the relationship between marriage and happiness, is the subject of replication in this paper.
+
 # Introduction
+
+In the spirit of reproducible science, a replication of the paper "Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)" [@marriagehappiness] is conducted according to the ReScience standards.
+ReScience defines replication as:
+
+>"a scientific study (computational or other) means repeating a published protocol, respecting its spirit and intentions but varying the technical details.
+For computational work, this would mean using different software, running a simulation from different initial conditions, etc.
+The idea is to change something that everyone believes shouldn’t matter, and see if the scientific conclusions are affected or not" [@rescience].
+
+This replication is unique because it is a replication of a replication.
+The first paper, "Income Inequality and Happiness" [@incomeinequality], is a study on happiness and specifically focuses on income equality.
+The study makes the conclusion that in years where there is greater income inequality in America, people are less happy.
+The paper attributes this negative relationship to meta variables such as perceived trust and perceived fairness in society.
+The second paper [@marriagehappiness] calls into question the data and the conclusions used by this study.
+The second paper replicates the first factoring in additional data like race, gender, and marriage to test for possible confounding variables.
+Most noteably, a relationship between marital status (single vs married) results in the only significant factor of a linear regression using all variables.
+In essence, the second paper makes the claim that when controlling for marriage, there is no relationship between income inequality and the happiness of Americans - invalidating the first paper's results.
+
+This paper will now be a second replication, focused on critiquing the methods and traceability of the second paper.
+Throughout the analysis, some critical pieces of missing data led to challenges in reproducing the results.
+In an effort to reproduce results, we had to find our own data and sources to tie in for the analysis.
 
@@
 
-There is a crisis of reproducibility and replication in the data science field.
-In an attempt to bolster confidence in scientific results, the following paper is a replication of "Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)" [@marriagehappiness].
-This paper follows the ReScience replication method[@rescience] which strongly encourages open source practices as underlined by the format of this project: a github compendium.
-This particular replication is unique in that the paper being replicated is an alternate implementation of the paper:"Income Inequality and Happiness" [@incomeinequality].
-While the first paper draws a connection between happiness and income, the second calls into question the data used to obtain the results stated, and pulls in additional data to re-assess the analysis.
-This second analysis, which focused on the relationship between marriage and happiness, is the subject of replication in this paper.
-
 # Methods
@@
 The dataset from gssr contained a larger time interval than the original paper.
-It was filtered back to match the original interval.
-Only years prior to 2008 are used in both analyses.
-This dataset was also merged with the original US Census Bureau data found in Gini_families.csv[@data] by appending the "total" column to the GSS data using "year" as the join key.
+It was filtered back to match the original interval so that only years prior to 2008 are used in both analyses.
+The new dataset was subsequently merged with the original US Census Bureau data found in Gini_families.csv[@data] by appending the "total" column to the GSS data using "year" as the join key.
 
@@
 
-Aside from gathering the input data from a new source, several different packages were used in addition to ensure the reproduced results were adequately tested.
-These will be discussed further in the respective sections below.
+Aside from gathering the input data from a new source, several different packages were used to ensure the reproduced results were adequately tested.
+These will be discussed further in their respective sections below.
 
@@
 
-Table 1 in the original publication explores the correlations between happiness and various control variables found in the dataset.
+Table 1 in the original publication explored the correlations between happiness and various control variables found in the dataset.
 
@@
 
-The R function cor.test() was used to get the Pearson correlation coefficient between the different independent variables (income on a log scale, age, sex, white, married) and the response variable, happiness.
+The R function cor.test() was used to get the Pearson correlation coefficient between the different independent variables (income on a log scale, age, sex, race, married) and the response variable, happiness.
 Grundberg et al.'s code was slightly modified to keep the same encoding of variables given the new dataset input.
@@
 
-We were able to almost exactly reproduce the results from Table 1 in the original paper that shown in Figure \@ref(fig:table1).
-The only difference is the estimate for Sex was 0.01 in the publication compared to 0.00 in our replication.
+We were able to almost exactly reproduce the results from Table 1 in the original paper as shown in Figure \@ref(fig:table1).
+The only difference being that the estimate for Sex was 0.01 in the publication compared to 0.00 in our replication.
 This may be due to rounding versions or an underlying exclusion of outliers we saw with the above plot.
@@
 There are several differences with the number of observations, listed in the bottom of the table, which is to be expected as we are using a package with the GSS data and it is likely not an identical snapshot to the one used in the original paper.
-However, this variability is minor in scale.Even though slight variabilities were observed in different cells throughout this table, no disparities were large enough to impact the significance of the results as denoted in the tables with asterisks.
+However, this variability is minor in scale.
+Even though slight variabilities were observed in different cells throughout this table, no disparities were large enough to impact the significance of the results as denoted in the tables with asterisks.
 Therefore, even with new data sources we found that the conclusions hold for the linear model analysis.
@@
 Under conditions of both a new source dataset and different R packages used for data manipulation and visualization, the 3 exhibits in the original publication were able to be replicated.
-With only minor discrepancies in the numbers themselves, the conclusions drawn from the paper's graphics were not significantly altered by any means.
+With only minor discrepancies in the numbers themselves, the conclusions drawn from the paper's graphics were not significantly altered.
 Successful replication of this paper is largely a result of transparency in the original publication providing clarity around data encoding and the models used for analysis.

### 2020-02-24 analysis/paper.Rmd
functionized plot for dynamic plotting

@@
 
-# write a function
+# Function to demonstrate that we can write a function.  In this case, this function creates a neat ggplot based on
+  # input for the data, x and y axes, factor, title, and x and y labels
+study_plotter <- function(plot_data, x_input, y_input, factor_input,
+                          factor_title_input = factor_input,
+                          factor_labs_input = NULL,
+                          title_input = paste0("Plot of ", x_input, " by ", y_input), 
+                          xlab_input = x_input, 
+                          ylab_input = y_input,
+                          caption_input = NULL,
+                          ylim_input){
+
+  # Evaluate the combination of the data and the x_input, y_input, and factor_input (allows for dynamic plotting)
+  x_input_eval <- eval(parse(text = paste0(plot_data, "$", x_input)))
+  y_input_eval <- eval(parse(text = paste0(plot_data, "$", y_input)))
+  factor_input_eval <- eval(parse(text = paste0(plot_data, "$", factor_input)))
+
+  # Set plot params
+  g <- ggplot(eval(as.name(plot_data)), aes(x = x_input_eval, y = y_input_eval, color = factor(factor_input_eval)))
+
+  # add plot elements and plot
+  g + geom_point(size = .6) +
+    geom_line(stat = "smooth",
+              method = "lm", 
+              se = FALSE, 
+              alpha = 0.5) +
+    theme_bw() +
+    labs(title = title_input,
+         x = xlab_input,
+         y = ylab_input,
+         caption = caption_input) +
+    scale_color_manual(values=c("blue", "forestgreen", "dodgerblue"),
+                       name=factor_title_input,
+                       breaks=c(1, 2, 3),
+                       labels=factor_labs_input) +
+    coord_cartesian(ylim = ylim_input) # setting this to match the study excludes the lm via the above methodology
+}
 
@@
 # Fig 3 reproduction
-g <- ggplot(race_summary, aes(x = year, y = happy_avg, color = factor(race)))
-g + geom_point(size = .6) +
-  geom_line(stat = "smooth",
-            method = "lm", 
-            se = FALSE, 
-            alpha = 0.5) +
-  theme_bw() +
-  labs(title = "Average Happiness by Race Trend",
-       x = "Year",
-       y = "Mean Happiness",
-       caption = "Figure 3") +
-  scale_color_manual(values=c("blue", "forestgreen", "dodgerblue"),
-                     name="Race",
-                     breaks=c(1, 2, 3),
-                     labels=c("White", "Black", "Other")) +
-  coord_cartesian(ylim = c(1.9,2.5)) # setting this to match the study excludes the lm via the above methodology
+
+study_plotter(plot_data = "race_summary", 
+              x_input = "year", 
+              y_input = "happy_avg", 
+              factor_input = "race",
+              factor_title_input = "Race",
+              factor_labs_input = c("White", "Black", "Other"),
+              title_input = "Trend of Average Happiness in the US by Race",
+              xlab_input = "Year",
+              ylab_input = "Mean Happiness",
+              caption_input = "Figure 3",
+              ylim_input = c(1.9,2.5))
+
 ```

### 2020-03-09 analysis/paper.Rmd
Changes output to pdf so recreated tables can render properly

@@
 date: "`r format(Sys.time(), '%d %B, %Y')`"
-output: bookdown::word_document2
+output: pdf_document
 bibliography: bibliography.bibtex
@@
 
-```{r, table1-replication, fig.cap="Replication of Table 1", echo=FALSE}
-knitr::include_graphics("table_1.png")
-```
-
 We were able to almost exactly reproduce the results from Table 1 in the original paper as shown in Figure \@ref(fig:table1).
@@
 
-The steps taken to reproduce this table are identical to those in the original publication aside from a new input dataset and the use of a combination of the kableExtra and xtable R packages to produce the output compared with xtable alone used in the original publication.
+The steps taken to reproduce this table are nearly identical to those in the original publication aside from a new input dataset.
 
@@
 ```{r display-table-2, eval=TRUE, results='asis'}
-```
-
-```{r, table2-replication, fig.cap="Replication of Table 2", echo=FALSE}
-knitr::include_graphics("table_2.png")
 ```

### 2020-03-09 analysis/001-creates-table-1.R

@@ -3,19 +3,21 @@
   require(Hmisc)
   require(Matrix)
   require(lme4)
+  library(xtable)
   library(gssr)
-  library(kableExtra)
-  
+
   data(gss_all)
   happy = gss_all
-  
+
   happy$Happiness = recode(happy$happy, "1=3; 3=1; c(0,8,9)=NA")
+  happy$TRUSTrecode = recode(happy$trust, "1=3; 2=1; 3=2; c(0,8,9)=NA")
+  happy$FAIRrecode = recode(happy$fair, "2=3; 3=2; c(0,8,9)=NA")
   happy$Age = recode(happy$age, "c(9)=NA")
   happy$REALINCrecode = recode(happy$realinc, "0=NA")
   happy$REALINClog = log(happy$REALINCrecode)
   happy$White = as.numeric(happy$race==1)
   happy$Married = as.numeric(happy$marital==1)
-  
+
   origData = happy[happy$year<=2008,]
 
 # ---- create-the-correlations-and-table
@@ -24,7 +26,7 @@
   sex = cor.test(origData$sex, origData$Happiness)
   race = cor.test(origData$White, origData$Happiness)
   marital = cor.test(origData$Married, origData$Happiness)
-  
+
   Estimate = round(c(income$estimate,age$estimate,sex$estimate,race$estimate,marital$estimate),3)
   p = round(c(income$p.value,age$p.value,sex$p.value,race$p.value,marital$p.value),3)
   table1 = as.data.frame(cbind(Estimate,p))
@@ -32,7 +34,4 @@
   rownames(table1) = c("Logged Income", "Age", "Sex", "White", "Married")
 
 # ---- display-table-1
-  knitr::kable(x=table1, "html", booktabs = TRUE, linesep = "") %>% 
-    kable_styling(full_width = FALSE, font_size = 12) %>% 
-    column_spec(1, width = "4cm") %>% 
-    save_kable(file = "table_1.png")
+  print(xtable(x=table1), type="latex", comment=FALSE)

### 2020-03-09 analysis/002-creates-table-2.R

@@ -6,14 +6,13 @@
   library(xtable)
   library(gssr)
   library(stargazer)
-  library(kableExtra)
-  
-  Gini = read.csv("../data/Gini_families.csv")
+
+  Gini = read.csv("data/Gini_families.csv")
   data(gss_all)
   happy = gss_all
   happy$Year = happy$year
   happy = merge(happy, Gini, by="Year")
-  
+
   happy$Happiness = recode(happy$happy, "1=3; 3=1; c(0,8,9)=NA")
   happy$Age = recode(happy$age, "c(9)=NA")
   happy$REALINCrecode = recode(happy$realinc, "0=NA")
@@ -23,32 +22,26 @@
   happy$Gini = happy$Total
 
   origData = happy[happy$Year<=2008,]
-  
+
 # ---- run-the-regressions
   m1 = lmer(Happiness ~ Gini + (1 | Year), data=origData)
   ci.m1 = confint(m1)
-  
+
   m2 = lmer(Happiness ~ Gini + REALINClog + (1 | Year), data=origData)
   m2.ci = confint(m2)
-  
+
   m3 = lmer(Happiness ~ Gini + Age + (1 | Year), data=origData)
   m3.ci = confint(m3)
-  
+
   m4 = lmer(Happiness ~ Gini + factor(sex) + (1 | Year), data=origData)
   m4.ci = confint(m4)
-  
+
   m5 = lmer(Happiness ~ Gini + White + (1 | Year), data=origData)
   m5.ci = confint(m5)
-  
+
   m6 = lmer(Happiness ~ Gini + Married + (1 | Year), data=origData)
   m6.ci = confint(m6)
 
 # ---- display-table-2
-  output <- stargazer(m1,m2,m3,m4,m5,m6, type="text")
-  
-  knitr::kable(x=output, "html", booktabs = TRUE, linesep = "&&") %>% 
-    kable_styling(full_width = FALSE, font_size = 12) %>% 
-    column_spec(1, width = "4cm") %>% 
-    save_kable(file = "table_2.png")
+  stargazer(m1,m2,m3,m4,m5,m6)
 
-  

### 2020-03-09 analysis/002-creates-table-2.R
Fixes file path to read from paper directory

@@ -7,7 +7,7 @@
   library(gssr)
   library(stargazer)
 
-  Gini = read.csv("data/Gini_families.csv")
+  Gini = read.csv("../data/Gini_families.csv")
   data(gss_all)
   happy = gss_all
   happy$Year = happy$year

### 2020-03-15 analysis/paper.Rmd
Adding compendium

@@
 link-citations: yes
-
 ---
@@
 # The Gini indices come from the provided dataset
-gini <-  read.csv("../data/Gini_families.csv") %>%
+gini <-  read.csv("data/Gini_families.csv") %>%
   select(year = Year, gini = Total)
@@
 
-```{r, figure3, fig.cap="Figure 3 from the original paper", echo=FALSE}
+```{r, figure3, fig.cap="Figure 3 from the original paper", out.width="400px", echo=FALSE}
 knitr::include_graphics("original_paper_figure_3.png")

### 2020-03-15 R/hello.R

@@ -1,0 +1,29 @@
+#' Add
+#'
+#' Adds two numbers
+#'
+#' @param a the first number
+#' @param b the second number
+#'
+#' @return The sum of two numbers
+#' @export
+#'
+#' @examples
+#' add(2, 3)
+add <- function(a, b) {
+  return(a + b);
+}
+
+#' Substracts two numbers
+#'
+#' @param a the first number
+#' @param b the number to substract
+#'
+#' @return The difference of two numbers (a-b)
+#' @export
+#'
+#' @examples
+#' substract(4, 2)
+substract <- function(a, b) {
+  return(a - b);
+}

### 2020-03-15 analysis/002-creates-table-2.R

@@ -7,7 +7,7 @@
   library(gssr)
   library(stargazer)
 
-  Gini = read.csv("../data/Gini_families.csv")
+  Gini = read.csv("data/Gini_families.csv")
   data(gss_all)
   happy = gss_all
   happy$Year = happy$year

### 2020-03-15 tests/testthat.R

@@ -1,0 +1,4 @@
+library(testthat)
+library(reScienceMarriageAndHappinessPkg)
+
+test_check("reScienceMarriageAndHappinessPkg")

### 2020-03-15 tests/testthat/test-hello.R

@@ -1,0 +1,9 @@
+context("add function")
+test_that("adding integers work", {
+  expect_equal(add(1, 2), 3)
+})
+
+context("substract function")
+test_that("substracting integers work", {
+  expect_equal(substract(4,3), 1)
+})

### 2020-03-15 analysis/fig3_reproduction.R
Removed unused files

@@ -1,35 +1,0 @@
-require(car)
-require(Hmisc)
-require(Matrix)
-require(lme4)
-library(xtable)
-library(gssr)
-
-Gini = read.csv("../data/Gini_families.csv")
-#happy = read.table("sub-data.txt", header=T, sep=",")
-data(gss_all)
-happy = gss_all
-happy = merge(happy, Gini, by.x = "year", by.y = "Year")
-
-# recode the GSS variables
-happy$Happiness = car::recode(happy$happy, "1=3; 3=1; c(0,8,9)=NA")
-happy$White = as.numeric(happy$race==1)
-happy$Married = as.numeric(happy$marital==1)
-
-whitebyYear = (aggregate(Happiness ~ year, data=happy[happy$race==1,], FUN=mean))
-blackbyYear = (aggregate(Happiness ~ year, data=happy[happy$race==2,], FUN=mean))
-otherbyYear = (aggregate(Happiness ~ year, data=happy[happy$race==3,], FUN=mean))
-plot(whitebyYear$year, whitebyYear$Happiness, ylim=c(1.9,2.5), pch=20, col="blue",
-     ylab="Mean Happiness", xlab="Year")
-abline(lm(Happiness ~ year, data=whitebyYear), col="blue")
-par(new=T)
-plot(whitebyYear$year, blackbyYear$Happiness, ylim=c(1.9,2.5), pch=20, col="forestgreen",
-     ylab="", xlab="")
-abline(lm(Happiness ~ year, data=blackbyYear), col="forestgreen")
-par(new=T)
-plot(whitebyYear$year, otherbyYear$Happiness, ylim=c(1.9,2.5), pch=20, col="dodgerblue",
-     ylab="", xlab="")
-abline(lm(Happiness ~ year, data=otherbyYear), col="dodgerblue")
-legend("bottomleft", legend=c("White", "Black", "Other"), col=c("blue", "forestgreen", "dodgerblue", lty=1, pch=20))
-mtext("Figure 3. Scatter plot (with best-fitting regression lines) showing mean happiness scores
-      for respondents identified as White, Black, or another race, from 1972 to 2008", 1, 4.25, cex = .6)

### 2020-03-15 replication.R

@@ -1,210 +1,0 @@
-rm(list=ls())
-require(car)
-require(Hmisc)
-require(Matrix)
-require(lme4)
-library(xtable)
-library(gssr)
-
-# load the data
-Gini = read.csv("data/Gini_families.csv")
-#happy = read.table("sub-data.txt", header=T, sep=",")
-data(gss_all)
-happy = gss_all
-happy$Year = happy$year
-happy = merge(happy, Gini, by="Year")
-
-# recode the GSS variables
-happy$Happiness = recode(happy$happy, "1=3; 3=1; c(0,8,9)=NA")
-happy$TRUSTrecode = recode(happy$trust, "1=3; 2=1; 3=2; c(0,8,9)=NA")
-happy$FAIRrecode = recode(happy$fair, "2=3; 3=2; c(0,8,9)=NA")
-happy$Age = recode(happy$age, "c(9)=NA")
-happy$REALINCrecode = recode(happy$realinc, "0=NA")
-happy$REALINClog = log(happy$REALINCrecode)
-happy$White = as.numeric(happy$race==1)
-happy$Married = as.numeric(happy$marital==1)
-happy$Gini = happy$Total
-
-# create two data sets, one for original data used in the paper (through 2008)
-# and another for the full data set (now available through 2012)
-origData = happy[happy$Year<=2008,]
-fullData = happy
-
-#### replicate multilevel model, Gini and happiness: Model 1
-m1 = lmer(Happiness ~ Gini + (1 | Year), data=origData)
-summary(m1)
-ci.m1 = confint(m1)
-
-#### Figure 1. Pattern over time of inequality, race, marital status
-png(file='Figure1.png', units='in', width=11, height=8.5, res=400)
-par(mfrow=c(2,2))
-#inequality
-giniByYear = Gini[Gini$Year>=1972,]
-plot(giniByYear$Year,giniByYear$Total, type="o", pch=20, xlab="Year",
-     ylab="Gini Coefficient", xaxt="n", ylim=c(.3, .46))
-axis(1, at=seq(1947,2012,by=5),labels=seq(1947,2012,by=5))
-
-#race
-raceByYear = aggregate(White ~ Year, FUN=mean, data=fullData)
-plot(happyByYear$Year, raceByYear$White, type="o", pch=20, xlab="Year",
-     ylab="Proportion White Respondents", xaxt="n", ylim=c(.65, .95))
[…]

### 2020-03-15 R/hello.R
updated hello.R to contain our plotting function with roxygen-style documentation

@@ -1,29 +1,54 @@
-#' Add
+# Function to demonstrate that we can write a function.  In this case, this function creates a neat ggplot based on
+# input for the data, x and y axes, factor, title, and x and y labels
+#' Title
 #'
-#' Adds two numbers
+#' @param plot_data data with 3 columns: a dependent, independent, and controlling factor
+#' @param x_input time-series such as year
+#' @param y_input independent var such as % happy
+#' @param factor_input factor to split the y_input such as race
+#' @param factor_title_input label for the factor title
+#' @param factor_labs_input labels for factors
+#' @param title_input plot title
+#' @param xlab_input x label
+#' @param ylab_input y label
+#' @param caption_input caption
+#' @param ylim_input upper and lower bounds e.g. c(1.9,2.5)
 #'
-#' @param a the first number
-#' @param b the second number
-#'
-#' @return The sum of two numbers
+#' @return a plot of the data with a linear regression per factor
 #' @export
 #'
 #' @examples
-#' add(2, 3)
-add <- function(a, b) {
-  return(a + b);
-}
+study_plotter <- function(plot_data, x_input, y_input, factor_input,
+                          factor_title_input = factor_input,
+                          factor_labs_input = NULL,
+                          title_input = paste0("Plot of ", x_input, " by ", y_input),
+                          xlab_input = x_input,
+                          ylab_input = y_input,
+                          caption_input = NULL,
+                          ylim_input){
 
-#' Substracts two numbers
-#'
-#' @param a the first number
-#' @param b the number to substract
-#'
-#' @return The difference of two numbers (a-b)
-#' @export
-#'
-#' @examples
-#' substract(4, 2)
-substract <- function(a, b) {
-  return(a - b);
+  # Evaluate the combination of the data and the x_input, y_input, and factor_input (allows for dynamic plotting)
+  x_input_eval <- eval(parse(text = paste0(plot_data, "$", x_input)))
+  y_input_eval <- eval(parse(text = paste0(plot_data, "$", y_input)))
+  factor_input_eval <- eval(parse(text = paste0(plot_data, "$", factor_input)))
+
+  # Set plot params
+  g <- ggplot(eval(as.name(plot_data)), aes(x = x_input_eval, y = y_input_eval, color = factor(factor_input_eval)))
+
+  # add plot elements and plot
+  g + geom_point(size = .6) +
+    geom_line(stat = "smooth",
+              method = "lm",
+              se = FALSE,
[…]

### 2020-03-16 R/hello.R
Removed % from hello.R causing build break.

@@ -1,10 +1,11 @@
-# Function to demonstrate that we can write a function.  In this case, this function creates a neat ggplot based on
-# input for the data, x and y axes, factor, title, and x and y labels
-#' Title
+#' study_plotter
+#'
+#' In this case, this function creates a neat ggplot based on
+#' input for the data, x and y axes, factor, title, and x and y labels
 #'
 #' @param plot_data data with 3 columns: a dependent, independent, and controlling factor
 #' @param x_input time-series such as year
-#' @param y_input independent var such as % happy
+#' @param y_input independent var such as \% happy
 #' @param factor_input factor to split the y_input such as race
 #' @param factor_title_input label for the factor title
 #' @param factor_labs_input labels for factors
@@ -16,8 +17,6 @@
 #'
 #' @return a plot of the data with a linear regression per factor
 #' @export
-#'
-#' @examples
 study_plotter <- function(plot_data, x_input, y_input, factor_input,
                           factor_title_input = factor_input,
                           factor_labs_input = NULL,

### 2020-03-16 tests/testthat/test-hello.R

@@ -1,9 +1,0 @@
-context("add function")
-test_that("adding integers work", {
-  expect_equal(add(1, 2), 3)
-})
-
-context("substract function")
-test_that("substracting integers work", {
-  expect_equal(substract(4,3), 1)
-})
